\plaintitle

### 2017-06-20 papers/IoT2017/intro.tex
updates

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodians of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.

@@

This paper assumes the existence of a distributed IoT infrastructure
and focuses on the following privacy challenges:
\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Inference of Future States of a Prosumer} 
  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Personally Identifiable Information} 
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple usage data collected by smart
  meters.  Specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy systems can be deployed widely in practice,
we must address the privacy issues described above. However, addressing these
issues is hard since solutions must also satisfy security
and safety requirements, which often conflict with privacy goals.  For
example, to prevent a prosumer from destabilizing the grid through
careless of malicious energy trading, the system must check all of the
prosumer's transactions.  In a decentralized system, this requires
disseminating information, which could be used to infer the prosumer's
future energy consumption.

In this paper, we \change{describe an overview of the transactive sequence between different components of the systems. We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate trading and enforce certain
safety rules. 
%
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce PETra and describe the
transactions and services used to implement it.  We then
discuss how PETra satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

>>>>

Power grids are undergoing major changes due to rapid acceleration in
renewable energy resources, such as wind and solar power
\cite{5430489}.
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
The massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in
an open market, trading and exchanging generated energy
locally. \emph{Distribution System Operators} (DSOs) can be the
custodians of this market, while still meeting the net demand
\cite{7462854}. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy developed by LO3 Energy as a pilot project.

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as IoT
applications in smart grids~\cite{Haider2016166}. The transactive grid
described in this paper is the next step in the evolution of energy
systems \cite{collier2017emerging}.

@@

This paper assumes the existence of a distributed IoT infrastructure
and focuses on the following privacy challenges:
\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
\item \textbf{Leakage of energy usage patterns to other prosumers}
  Since prosumers may purchase energy from each other in a transactive
  microgrid, transactions may inadvertently reveal the prosumers'
  detailed energy usage patterns to other prosumers within the
  microgrid.  Addressing this issue in a decentralized trading system
  is hard as it requires hiding the identities of trade partners from
  each other. In comparison, secure smart metering reveals the
  prosumers' energy usage patterns only to the operator.

\item \textbf{Inference of future states of a prosumer} Transactions
  may reveal the future energy usage of a prosumer, which could be
  used to infer private information.  For example, a smart home may
  know that its inhabitants will go out in the evening (\emph{e.g.},
  by looking at their calendar), and it may trade energy futures
  accordingly in the morning.  Without adequate privacy measures,
  these trades may reveal to other prosumers in the microgrid that the
  inhabitants will not be at home later.  Note that energy futures,
  whose delivery may happen several hours after when the transaction
  is made, can play an important role in predicting and controlling
  microgrid load.  In comparison, smart metering reveals only current
  (or past) usage.

\item \textbf{Personally identifiable information} Transactions and
  energy usage data in a transactive microgrid are much richer sources
  of information than the simple usage data collected by smart meters.
  In particular, the information available in a transactive microgrid
  is a superset of what is available from smart metering and may be
  used to infer personal information, such as risk propensity and
  financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy systems can be deployed widely in practice,
the privacy issues described above must be addressed.  Addressing
these issues is hard, however, since solutions must also satisfy
security and safety requirements, which often conflict with privacy
goals.  For example, to prevent a prosumer from destabilizing the
system through careless of malicious energy trading, a transactive
grid must check all of the prosumer's transactions.  In a
decentralized system, these checks require disseminating information,
which could be used to infer the prosumer's future energy consumption.

This paper describes an overview of the transactive sequence between
different components of the systems. We also describe the structure of
these transactions and show how they can be used to provide
\emph{Privacy-preserving Energy Transactions} (PETra). PETra is our
distributed-ledger based solution that (1) enables trading energy
futures in a secure and verifiable manner, (2) preserves prosumer
privacy, and (3) enables DSOs to regulate trading and enforce certain
safety rules.

% \Aron{Since SIGCHI does not have section numbers, this paragraph,
%  which describes the organization of the paper, is not very clear.}
The remainder of this paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how PETra satisfies the security, safety, and privacy
requirements; finally we compare our work on PETra with related work
and present concluding remarks.

### 2017-06-20 papers/IoT2017/paper.tex
updates

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

>>>>

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which arrange local
communities into transactive microgrids.  Within a transactive
microgrid, ``prosumers'' (i.e., consumers with energy generation and
storage capabilities) can trade energy with each other, thereby
smoothing the load on the main grid using local supply.  It is hard,
however, to provide security, safety, and privacy in a decentralized
and transactive energy system.  On the one hand, prosumers' personal
information must be protected from their trade partners and the system
operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving
    Energy Transactions} (PETra)}, which is secure and safe solution
for transactive microgrids that enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra}
builds on distributed ledgers, such as blockchains, and provides
anonymity for communication, bidding, and trading.
\end{abstract}

### 2017-06-20 papers/IoT2017/prelim.tex
updates

\change{This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.}{A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them. A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer. Additionally, the microgrid contains a set of 
protection nodes that are  responsible for isolating faults on the feeder. Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system. The DSO is responsible for regulating the net electric power into and out of the microgrid. Starting from this model, we next introduce the transactive microgrid model.}

\subsection{Transactive Microgrid System Model}
\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
We describe a basic system model of decentralized 
\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.
Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
\change{our solution.  In this figure, components marked red are introduced to
provide privacy in a safe and secure manner, whereas components marked
in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
Components marked in blue are basic elements of the decentralized transactive microgrid,
while components marked in red are added (or extended) by PETra.}

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{High-level architecture of a decentralized transactive microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}

\subsubsection{Distributed Ledger}
This ledger permanently stores transactions that specify energy
trades, change regulatory policies for the microgrid, etc.  For
providing security and safety, it is crucial that transactions are
immutable, \emph{i.e.}, after a transaction has been recorded, it
cannot be modified or removed from the ledger.  To enhance fault
tolerance, however, the ledger should also be distributed.

@@

\subsubsection{Privacy} 
Privacy requirements ensure that the prosumers' privacy is not
compromised when they participate in energy trading.  We use
non-transactive smart metering as a baseline, and we require that
the transactive system does not leak any additional information
compared to this baseline.  More specifically, we require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item only the corresponding smart meter and the DSO may gain
  information regarding the amount of energy produced, consumed,
  bought, or sold by a prosumer,\footnote{Note that this requirement
    is impossible to satisfy if all other prosumers may collude
    against one target. However, we can assume that the majority of
    prosumers are non-colluding.}
\item only the prosumer may know which bids and asks it has posted,
  and no one can know who traded energy with whom.
\end{itemize}

>>>>

This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.
A microgrid is a collection of prosumers (residential nodes) that are
arranged within the same distribution feeder and support exchange of
power between them. A prosumer node typically includes a smart
inverter and a smart meter, which control the flow of power into and
out of the prosumer.

A microgrid also typically contains a set of protection nodes that are
responsible for isolating faults on the feeder.  The
\emph{Distribution System Operator} (DSO) operations a set of
switching nodes to control the connection of the microgrid to the rest
of the distribution system. The DSO is responsible for regulating the
net electric power into and out of the microgrid. Starting from this
model, we next introduce the transactive microgrid model.

\subsection{Transactive Microgrid System Model}
\Abhishek{This is the perfect paragraph to define transactive
  microgrid as a special application of IoT spread over a large
  area. Perhaps we can find a citation that makes this point.}  We
describe a basic system model of decentralized transactive IoT
microgrids.  We discuss the following components: a distributed ledger
for recording transactions, a bid storage service that facilitates
finding trade partners, a microgrid controller for regulating the
microgrid load, and smart meters for measuring the prosumers' energy
production and consumption.

Figure~\ref{fig:softwareArchitecture} shows the a decentralized
transactive microgrid with PETra.  In this figure, components marked
red are introduced to provide privacy in a safe and secure manner,
whereas components marked in blue are typical elements of a
decentralized transactive microgrid.
\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{The Architecture of a Decentralized Transactive Microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}

\subsubsection{Distributed Ledger}
This ledger permanently stores transactions that specify energy
trades, change regulatory policies for the microgrid, etc.  For
providing security and safety, it is crucial that transactions be
immutable, \emph{i.e.}, after a transaction has been recorded, it
cannot be modified or removed from the ledger.  To enhance fault
tolerance, however, the ledger should also be distributed.

@@

\subsubsection{Privacy} 
Privacy requirements ensure that the prosumers' privacy is not
compromised when they participate in energy trading.  We use
non-transactive smart metering as a baseline, and we require that
the transactive system does not leak any additional information
compared to this baseline.  More specifically, we require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item only the corresponding smart meter and the DSO may gain
  information regarding the amount of energy produced, consumed,
  bought, or sold by a prosumer,\footnote{Although this requirement is
    impossible to satisfy if all other prosumers may collude against
    one target, we can assume that the majority of prosumers are
    non-colluding.}
\item only the prosumer may know which bids and asks it has posted,
  and no one can know who traded energy with whom.
\end{itemize}
